\documentclass[a4paper,12pt]{report}
\addtolength{\topmargin}{-0.8in}
\setlength\textheight{248mm}
\setlength\textwidth{165mm}
\setlength\oddsidemargin{-2mm}
\setlength\evensidemargin{-2mm}
\usepackage[english]{babel}
\usepackage[a-2u]{pdfx}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{lmodern,textcomp}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\usepackage{xcolor,colortbl}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{pgfplots}
\usepackage{multicol}
\usepackage{ulem}
\usepackage{color}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{setspace}
\usepackage{listings}
\usepackage{cancel}
\usepackage{marvosym}
\usepackage{multicol}
\usepackage{fancyvrb}

\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\graphicspath{ {../images/} }
\def\columnseprulecolor{\color{black}}
\setlength{\columnseprule}{0.3pt}
\def\title{Specification}
\def\author{Adam Beneš}
\setlength{\parindent}{0pt}
\def\doubleunderline#1{\underline{\underline{#1}}}\makeatletter
\def\@makechapterhead#1{
	{\parindent \z@ \raggedright \normalfont
		\huge\bfseries \thechapter. #1
		\par\nobreak
		\vskip 20\p@
}}
\def\@makeschapterhead#1{
	{\parindent \z@ \raggedright \normalfont
		\huge\bfseries #1
		\par\nobreak
		\vskip 20\p@
}}
\makeatother

\renewcommand{\chaptermark}[1]{%
	\markboth{#1}{}}

\fancypagestyle{toc}{
	\fancyhf{}
	\renewcommand{\headrulewidth}{0.4pt}
	\renewcommand{\footrulewidth}{0.4pt}
	\fancyhead[C]{}
	\fancyhead[L]{\textbf{\title}}
	\fancyfoot[L]{\author}
	\fancyfoot[C]{}
	\fancyfoot[R]{\thepage}
}

\fancypagestyle{plain}{
	\fancyhf{}
	\renewcommand{\headrulewidth}{0.4pt}
	\renewcommand{\footrulewidth}{0.4pt}
	\fancyhead[C]{}
	\fancyhead[L]{\textbf{\title\ -- \thechapter. \leftmark}}
	\fancyfoot[L]{\author}
	\fancyfoot[C]{}
	\fancyfoot[R]{\thepage}
}


\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=false,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}

\lstset{style=mystyle}

\begin{document}
	\pagenumbering{roman}
	\addtocontents{toc}{\protect\thispagestyle{toc}}
	\pagestyle{toc}
	\tableofcontents
	\cleardoublepage
	\pagestyle{plain}
	\pagenumbering{arabic}
	\pagebreak
	
	\chapter{Introduction}
	
	\section{Rough specification of the project}
	
	Create an election processing program with different election rules, elections will be processed using streaming algorithms.
	
	\section{Where is the project stored}
	
	Project is stored at \href{https://gitlab.com/adam_b3n3s/vote_streams}{Gitlab} and at this \href{https://github.com/AdamBenes3/vote_streams}{Github}.
	
	\chapter{More detailed specifications}
	
	\section{Libraries}
	
	\begin{itemize}
		\item \href{https://github.com/PrefLib}{Preflib}.
		\item ...
	\end{itemize}
	
	\section{Resources}
	
	\begin{itemize}
		\item \href{http://dimacs.rutgers.edu/~graham/ssbd.html}{Book about streaming algorithms}.
		\item \href{https://dl.acm.org/doi/pdf/10.1145/198429.198435 }{Paper reservoir sampling}.
		\item \href{https://en.wikipedia.org/wiki/Reservoir_sampling}{Wiki reservoir sampling}.
		\item ...
	\end{itemize}
	
	\section{Algorithms}
	
	\begin{itemize}
		\item Misra-Gries algorithm.
		\item Reservoir sampling algorithms.
		\item ...
	\end{itemize}
	
	\section{Decomposition of the project}
	
	\subsection{File tree}
	
	\begin{itemize}
		\item src:
		
		Contains all source code.
		
		\item docs:
		
		Contains .tex files related to the project, specifications, user documentation, developer documentation. All at least in thesse languages:
		
		\begin{itemize}
			\item English.
		\end{itemize}
		
		\item test:
		
		Contains function tests in src.
	\end{itemize}
	
	\subsection{Dekomposition of src}
	
	\subsubsection{main.py}
	
	This is the main method it will read data from a file, call functions from other Python files that will contain individual voting stream algorithms, and more.
	
	\subsubsection{vote\_generator.py}
	
	This is a file that will generate choices, in various ways:
	
	\begin{itemize}
		\item Exponential distribution.
		\item Normal distribution (Gaussian curve).
		\item ...
	\end{itemize}
	
	\subsection{Files of individual election rules}
	
	In the file vote\_rules. It contains the implementation of individual election rules.
	
	\subsection{Sampling algorithms}
	
	Selection of smaller number of tickets.
	
	
	
	
	
	
	
	
	
	
	
	
\end{document}